Stochastic Convolutional Sparse Coding

### 2019-08-20 VMV19/Results.tex
small edits

\changed{ \subsection{Experimental Design}
We first validate the proposed algorithms on the fruit and city
datasets~\cite{zeiler2010deconvolutional}, where each consists of 10
training images of size $100 \times 100$. The online-mode algorithms
are then adapted to one thousand $100 \times 100$ image patches
randomly picked up from ImageNet~\cite{deng2009imagenet}. Note that batch-based CSC commonly can only handle less than 100 images
simultaneously due to the memory limitation. The dictionary size is set to $100$ filters of size $11 \times 11$ pixels in all experiments except for over-complete dictionary. All training and evaluation processes in this manuscript are performed on contrast normalized
images~\cite{zeiler2010deconvolutional,heide2015fast}.}

@@

{\bfseries Convergence.} Comparisons of the convergence between the
proposed method (SBCSC) and the state-of-the-art batch-mode
algorithm~\cite{heide2015fast} are shown in
Fig.~\ref{fig:subsampleResult} \changed{(the compared method uses a similar number of iterations as ours to reach convergence)}. A different selection of the
subsampling rate reveals that the proposed strategy will slightly
influence the convergence and the training objective of the
minimization problem. Specifically, the more subsampled, the
relatively slower convergence and the higher objective will be
obtained. On the other hand, small subsampling rate will significantly
accelerate the computation process, where $10\%$ subsampling achieves
about $6 \times$ speedup over the not subsampled spatial domain solver
and a $2 \times$ speedup over state-of-the-art Frequency-domain solver
for one iteration. We observe that a subsampling rate between $p=0.1$
and $p=0.2$ delivers empirically good enough convergence in our
settings, as well as achieving at least $3 \times$ speedup. In
general, the proposed method with various subsampling rates converges
at around 10-12 iterations in all testing cases, acting similar to the
competing methods.

>>>>

\changed{ \subsection{Experimental Design}
We first validate the proposed algorithms on the fruit and city
datasets~\cite{zeiler2010deconvolutional}, that each consist of 10
training images of size $100 \times 100$. The online-mode algorithms
are then adapted to one thousand $100 \times 100$ image patches
randomly picked up from ImageNet~\cite{deng2009imagenet}. Note that batch-based CSC commonly can only handle less than 100 images
simultaneously due to the memory limitation. The dictionary size is set to $100$ filters of size $11 \times 11$ pixels in all experiments except for over-complete dictionary. All training and evaluation processes in this manuscript are performed on contrast normalized
images~\cite{zeiler2010deconvolutional,heide2015fast}.}

@@

{\bfseries Convergence.} Comparisons of the convergence between the
proposed method (SBCSC) and the state-of-the-art batch-mode
algorithm~\cite{heide2015fast} are shown in
Fig.~\ref{fig:subsampleResult} \changed{(the comparison method uses a similar number of iterations as ours to reach convergence)}. A different selection of the
subsampling rate reveals that the proposed strategy will slightly
influence the convergence and the training objective of the
minimization problem. Specifically, the more subsampled, the
relatively slower convergence and the higher objective will be
obtained. On the other hand, small subsampling rate will significantly
accelerate the computation process, where $10\%$ subsampling achieves
about $6 \times$ speedup over the not subsampled spatial domain solver
and a $2 \times$ speedup over state-of-the-art Frequency-domain solver
for one iteration. We observe that a subsampling rate between $p=0.1$
and $p=0.2$ delivers empirically good enough convergence in our
settings, as well as achieving at least $3 \times$ speedup. In
general, the proposed method with various subsampling rates converges
at around 10-12 iterations in all testing cases, acting similar to the
competing methods.

### 2019-08-20 VMV19/SCSCmodel.tex
small edits

%The work of~\cite{mensch2016dictionary} also applies a so-called
%stochastic subsampling strategy for dictionary learning, where the
%subsampling is randomly performed on the observed signals, differing
%from that of our proposed. In addition, it is basically applied for
%factorizing matrix that is large in both dimensions. Although CSC can
%be expressed in a similar mathematical formula as matrix factorization, the two
%problems are in practice quite different due to the convolutional
%property of the CSC model.
\changed{Our proposed randomization approach shares a similar idea as utilized in the stochastic Frank-Wolfe
algorithm~\cite{reddi2016stochastic,pmlr-v80-kerdreux18a}.  The general idea of that is to solve the optimization problem on a subset of the variables at each iteration, which are
randomly extracted based on a certain probability distribution.} For the proposed algorithm, each iteration extracts
($pDK+MK$) variables, where $pDK$ variables are randomly picked from a
total $DK$ variables, and the rest remain unchanged. Owing to the fact
that CSC model is \changed{over-parameterized} and the codes are highly 
sparse, the original signals can still be represented by a portion of 
the codes under a reasonable subsampling
rate. Therefore, the convergence of the proposed algorithm will not be
significantly affected by the subsampling manipulation, unlike the
general case of the stochastic Frank-Wolfe algorithm, which usually
requires more iterations to reach convergence. This insight is
experimentally verified in Section~\ref{sec:result}.

>>>>

%The work of~\cite{mensch2016dictionary} also applies a so-called
%stochastic subsampling strategy for dictionary learning, where the
%subsampling is randomly performed on the observed signals, differing
%from that of our proposed. In addition, it is basically applied for
%factorizing matrix that is large in both dimensions. Although CSC can
%be expressed in a similar mathematical formula as matrix factorization, the two
%problems are in practice quite different due to the convolutional
%property of the CSC model.
\changed{Our proposed randomization approach utilizes ideas similar to the stochastic Frank-Wolfe
algorithm~\cite{reddi2016stochastic,pmlr-v80-kerdreux18a}.  The general idea is to solve the optimization problem on a subset of the variables at each iteration, which are
randomly extracted based on a certain probability distribution.} For the proposed algorithm, each iteration extracts
($pDK+MK$) variables, where $pDK$ variables are randomly picked from a
total $DK$ variables, and the rest remain unchanged. Owing to the fact
that CSC model is \changed{over-parameterized} and the codes are highly 
sparse, the original signals can still be represented by a portion of 
the codes under a reasonable subsampling
rate. Therefore, the convergence of the proposed algorithm will not be
significantly affected by the subsampling manipulation, unlike the
general case of the stochastic Frank-Wolfe algorithm, which usually
requires more iterations to reach convergence. This insight is
experimentally verified in Section~\ref{sec:result}.
